Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
paper: combine mantle bar graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-performance.png}
\caption{All CephFS balancing modes have the same performance Mantle uses a
balancer designed for sequencers.}\label{fig:mantle-balancer-performance}
\end{figure}

@@

Another factor that affects performance in this environment is ``how much" load
is on each server; these experiments quantify that effect by programming
policies into the load balancing interface to control the amount of load to
migrate. We define migration unit as the amount of load to try and migrate.
For example, it is useful to express migration units as a fraction of the total
load.  Expressing this heuristic is not easily achievable with outward facing
tunable parameters (i.e. system knobs) and so the original CephFS balancers do
not have a migration unit tunable.  With Mantle's programmable interface, we
force the load balancer into the Proxy Mode (Full) scenario in
Figure~\ref{fig:mantle-modes}, which sets the balancer to proxy mode with
migration units equal to the entire load on the current server we can use the Mantle
policy:\\

\noindent \texttt{ targets[\#mds+1] = mds[whoami]["load"] }\\

This code snippet uses globally defined variables and tables from the Mantle
API to send half of the load on the current server (whoami) to the next ranked
server (\#mds + 1); the \texttt{targets} array is a globally defined table that
the balancer uses to do the migrations. Alternatively, to set the mode to the
``Proxy (Half)"` setup in Figure~\ref{fig:mantle-modes} we can divide the right
hand side by 2.

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-performance.png}
\caption{The performance of the different modes using various migration units
shows almost a 2\(\times\) improvement in the best case.
}\label{fig:mantle-mode-performance}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-mode-performance.png}
\includegraphics{figures/mantle-balancer-performance.png}
\caption{All CephFS balancing modes have the same performance Mantle uses a
balancer designed for sequencers.}\label{fig:mantle-balancer-performance}
\end{figure}

@@

Another factor that affects performance in this environment is ``how much" load
is on each server; these experiments quantify that effect by programming the
load balancing interface to control the amount of load to migrate. We call this
metric a ``migration unit".  Expressing this heuristic is not easily achievable
with outward facing tunable parameters (i.e. system knobs) but with Mantle's
programmable interface, we can force the load balancer to change its migration
units. To force the balancer into the Proxy Mode (Half) scenario in
Figure~\ref{fig:mantle-modes}, which uses migration units that are half the
load on the current server:\\

\noindent \texttt{ targets[whoami+1] = mds[whoami]["load"]/2 }\\

This code snippet uses globally defined variables and tables from the Mantle
API to send half of the load on the current server (whoami) to the next ranked
server (whoami + 1); the \texttt{targets} array is a globally defined table that
the balancer uses to do the migrations. Alternatively, to migrate all load a
time step, we can remove the division by 2.

%\begin{figure}[t!]
%\centering
%\includegraphics{figures/mantle-mode-performance.png}
%\caption{The performance of the different modes using various migration units
%shows almost a 2\(\times\) improvement in the best case.
%}\label{fig:mantle-mode-performance}
%\end{figure}
